---
title: "2020_11_29_hike"
author: "Pozdniakov Ivan"
date: "29 11 2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE, fig.height = 12)
```

## Dataset downloading and description

Today, we analyze [Washington Trails Association](https://www.wta.org/go-outside/hikes?b_start:int=1) data that were collected by [TidyX](https://bit.ly/TidyX_Ep35) crew. It can be downloaded from [Tidy Tuesday Github page](https://github.com/rfordatascience/tidytuesday/blob/master/data/2020/2020-11-24/readme.md) or by using `tidytuesdayR` package.

```{r}
library(tidyverse)
library(hrbrthemes)
tuesdata <- tidytuesdayR::tt_load('2020-11-24')
hike_data <- tuesdata$hike_data
```

## Preprocessing

```{r}
hike_clean <- hike_data %>%
  mutate(id = row_number(), .before = everything()) %>%
  separate(col = location, 
           into = c("region", "area"),
           sep = "\\s--\\s",
           fill = "right") %>%
  separate(col = length,
           into = c("length_miles", "type"),
           sep = "\\smiles,?\\s(?:of\\s)?") %>% 
  type_convert() %>%
  mutate(rating = na_if(rating, 0))
  
skimr::skim(hike_clean)  
```

We unnest list-column to long data and then use `pivot_wider()` to create new multiple columns.

```{r}
hike_long <- hike_clean %>%
  unnest(cols = features) 

hike_wide <- hike_long %>%
  mutate(value = TRUE) %>%
  pivot_wider(names_from = features, 
              values_from = value,
              values_fill = FALSE)
```

Then, we use across to calculate ratio by region on these multiple columns.

```{r}
features_ratio_by_region <- hike_wide %>%
  group_by(region) %>%
  summarise(across(`Dogs allowed on leash`:Summits, mean)) %>%
  pivot_longer(cols = `Dogs allowed on leash`:Summits,
               names_to = "features",
               values_to = "ratio") %>%
  arrange(region, features)
```

## Visualization

```{r}
features_ratio_by_region %>%
  ggplot() +
  geom_col(aes(x = region, y = ratio, fill = region)) +
  coord_polar(clip = "off") +
  facet_wrap(~features) +
  scale_y_continuous(labels = scales::percent, limits = c(0,1)) +
  guides(fill = FALSE) +
  labs(x = "",
       y = "",
       title = "Which region fits your hiking habits",
       subtitle = "Ratio of trail features by Washington regions",
       caption = "Created by Ivan Pozdniakov for Тайди Стрим\nData from 2020-11-24 Tidy Tuesday: https://www.tidytuesday.com") +
  theme_ipsum(base_size = 5)
```

